A semantics of core AUTOSAR

### 2016-08-16 paper/paper.tex
Added two examples.

The following example illustrates a scenario where a sent value is only stored in a subset of the connected buffers. Assuming $\Tconnect {\Tep e p i} a$ and $\Tconnect {\Tep e p i} b$:
$$
\begin{array}{c}
  \Trinst {i.r} c \Xs {\TrteSend {p.e} v k} \,\Opar  \\
  {\Tqelem a 2 \Teps} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}} \vspace{0.6ex} \\
  \red{\say{i.p.e}{\Tsnd v {a_2}}} \\
  \Trinst {i.r} c \Xs {\Tap k \Tlimit} \,\Opar \\
  {\Tqelem a 2 v} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}}
\end{array}
$$

@@

As an example, consider the example of Section~\ref{sect:BufSndRcv} under the different assumption that only $\Tconnect{{i.p.e} a}$ holds, with no connection from ${i.p.e}$ to $b$.
$$
\begin{array}{c}
  \Trinst {i.r} c \Xs {\TrteSend {p.e} v k} \,\Opar  \\
  {\Tqelem a 2 \Teps} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}} \vspace{0.6ex} \\
  \red{\say{i.p.e}{\Tsnd v \Teps}} \\
  \Trinst {i.r} c \Xs {\Tap k \Tok} \,\Opar \\
  {\Tqelem a 2 v} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}}
\end{array}
$$

\subsection{TODO}

@@

\section{Examples}
\label{sec:Examples}

\begin{itemize}
\item More details on the simple examples + a bigger example.
\item Some examples chosen to illustrate the value of a formal calculus
\end{itemize}

>>>>

The following example illustrates a scenario where a sent value is only stored in a subset of the connected buffers. Assuming $\Tconnect {\Tep e p i} a$ and $\Tconnect {\Tep e p i} b$:
$$
\begin{array}{c}
  \Trinst {i.r} c \Xs {\TrteSend {p.e} v k} \,\Opar  \\
  {\Tqelem a 2 \Teps} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}} \vspace{0.6ex} \\
  \red{\say{i.p.e}{\Tsnd v b}} \\
  \Trinst {i.r} c \Xs {\Tap k \Tlimit} \,\Opar \\
  {\Tqelem a 2 v} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}}
\end{array}
$$

@@

As an concrete illustration, consider the example of Section~\ref{sect:BufSndRcv}. The axioms that enable each individual process transition in that example are (26), (27) and (28), respectively (and rules (1) and (3) allow them to be combined). In particular, axiom (28) is applicable because of the assumption $\Tconnect {i.p.e} b$, which simultaneously blocks applicability of axiom (70). However, under the different assumption that there is no connection from ${i.p.e}$ to $b$, axioms (28) and (70) must trade places. This also forces the removal of $b$ from the second argument of the {\sc snd} payload (i.e., the list of connected buffers not able to store the value sent). As a consequence, axiom (26) is no longer applicable and must be replaced by axiom (25). The resulting parallel transition looks as follows, illustrating the correct generation of an {\bf ok} result despite the presence of a full (but unconnected) buffer.
$$
\begin{array}{c}
  \Trinst {i.r} c \Xs {\TrteSend {p.e} v k} \,\Opar  \\
  {\Tqelem a 2 \Teps} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}} \vspace{0.6ex} \\
  \red{\say{i.p.e}{\Tsnd v \Teps}} \\
  \Trinst {i.r} c \Xs {\Tap k \Tok} \,\Opar \\
  {\Tqelem a 2 v} \Opar {\Tqelem b 2 {\Tcons {v_1} {v_2}}}
\end{array}
$$

@@

\section{Parallelism}
\label{sec:Parallelism}

$$
\begin{array}{c}
  {\Trunnable a 0 \Tidle 0} \Opar 
  {\Tqelem b 2 \Teps} \vspace{0.6ex} \\

  \red{\hear{b}{\Tsnd {v_1} \Teps}} \\

  {\Trunnable a 0 \Tpending 0} \Opar 
  {\Tqelem b 2 {v_1}} \vspace{0.6ex} \\

  \red{\say{a}{\Tnew}} \\

  {\Trunnable a 0 \Tidle 1} \Opar 
  {\Tqelem b 2 {v_1}} \,\Opar  \\
  {\Trinst a \Tvoid \Teps {\Code}} \vspace{0.6ex} \\

  \red{\hear{b}{\Tsnd {v_2} \Teps}} \\

  {\Trunnable a 0 \Tpending 1} \Opar 
  {\Tqelem b 2 {\Tcons{v_1}{v_2}}} \,\Opar  \\
  {\Trinst a \Tvoid \Teps {\Code}} \vspace{0.6ex} \\

  \red{\say{a}{\Tnew}} \\

  {\Trunnable a 0 \Tidle 2} \Opar 
  {\Tqelem b 2 {\Tcons{v_1}{v_2}}} \,\Opar  \\
  {\Trinst a \Tvoid \Teps {\Code}} \Opar 
  {\Trinst a \Tvoid \Teps {\Code}}
\end{array}
$$

$$
\begin{array}{c}
  {\Trunnable a 0 \Tidle 0} \Opar 
  {\Tqelem b 2 \Teps} \vspace{0.6ex} \\

  \red{\hear{b}{\Tsnd {v_1} \Teps}} \\

  {\Trunnable a 0 \Tpending 0} \Opar 
  {\Tqelem b 2 {v_1}} \vspace{0.6ex} \\

  \red{\hear{b}{\Tsnd {v_2} \Teps}} \\

  {\Trunnable a 0 \Tpending 0} \Opar 
  {\Tqelem b 2 {\Tcons{v_1}{v_2}}} \vspace{0.6ex} \\

  \red{\say{a}{\Tnew}} \\

  {\Trunnable a 0 \Tidle 2} \Opar 
  {\Tqelem b 2 {\Tcons{v_1}{v_2}}} \,\Opar  \\
  {\Trinst a \Tvoid \Teps {\Code}}
\end{array}
$$
